---
title: "2025-01_Data check"
author: Dominick Terranova
date: 2025/01/27
format: pdf
editor_options: 
  chunk_output_type: console
---
# I do not understand why there are negatives in some of the day counts sums in the code you gave us, what does it mean if the number is negative?

This code changes how the code is displayed when rendered

```{r knitr, warning=FALSE, echo = FALSE, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE,
  require("knitr")
)
```

Import library

```{r, echo=FALSE, warning=FALSE, include=FALSE}
library(survival)
library(tidyverse)
library(tidymodels)
#library(ggsurvfit)
library(lubridate)
#library(ggfortify)
library(lmtest)

library(car)
library(poissonreg)

library(pscl)

library(broom)
library(broom.mixed)

library(readr)
library(skimr)
```

#### Check Erik and Brenton google sheet

Read in Data

```{r}
#| label: read-in

source("read_clean.R")
```

#### Check dates

This code chunk gives us how the sum of how many ibis_coverage_start_date is earlier than the coverage_start_date in the report_full data. (969)

```{r}
 sum(report_full$ibis_coverage_start_date < report_full$coverage_start_date)
```

This code chunk allows us acknowledge weird inputs in the starting and ending dates within the data. The results indicate that that the date "1969-12-31" could be some sort of filler date for patients because it does not make sense that every patient with this date input in their chart would have it as their start and end date.

```{r}
sum(ymd(report_full$event_end_date) == "1969-12-31")
sum(ymd(report_full$event_start_date) == "1969-12-31")
sum(ymd(report_full$ibis_coverage_start_date) == "1969-12-31")
sum(ymd(report_full$ibis_coverage_end_date) == "1969-12-31")
sum(ymd(report_full$last_reminder_complete_date) == "1969-12-31")
```

This is just to select only the columns we want.

```{r}
idx_0 <- which(names(report_full) == "condition_count") 
 idx_1 <- which(names(report_full) == "urologic_cancer") 
     
 patients <- report_full %>% select(pid, age, org_name, hcc, status, c(idx_0:idx_1)) 
 ## %>% distinct(pid, .keep_all = TRUE) 
```

Prints 421, indicating that there are 421 patients in the Unicare study.
```{r}
patients %>% filter(str_detect(org_name, "Unicare - Study"))  %>% nrow()
  #  filter(org_name == "Unicare - Study") %>% nrow()
```

Indicates there are 185,297 coverage days for Unicare members in the study pre Ibis admission
```{r}
sum(report_full$covered_days_pre_ibis[report_full$org_name == "Unicare - Study"])
```

Indicates there are 30,231 coverage days for Unicare members in the study post Ibis admission
```{r}
sum(report_full$covered_days_post_ibis[report_full$org_name == "Unicare - Study"])
```

Indicates there are 903,546 coverage days for all members pre Ibis admission
```{r}
sum(report_full$covered_days_pre_ibis)
```

Indicates there are 152,527 coverage days for all members post Ibis admission
```{r}
sum(report_full$covered_days_post_ibis)
```

This code chunk just confirms that each patient has their own unique ID
```{r}
unique(events_full$event_type) 

events_full %>% select(pid) %>% distinct()
```

\#### admits pre/post Create data with admission count
```{r}

#######
####### 

## pre ibis admissions count
pre_ibis_admissions_count <- events_full %>% filter(event_start_date  <= ibis_coverage_start_date) %>% filter(event_start_date >= coverage_start_date) %>%
    select(pid, event_type, event_start_date) %>%
    filter(event_type == "inpatient") %>%
    group_by(pid) %>% summarize(admit_count = n()) %>% 
    right_join(patients, by = "pid") %>% mutate(admit_count = ifelse(is.na(admit_count), 0, admit_count))


## post ibis admissions count
post_ibis_admissions_count <- events_full %>% filter(event_start_date > ibis_coverage_start_date) %>% filter(event_start_date <= ibis_coverage_end_date) %>%
    select(pid, event_type, event_start_date) %>%
    filter(event_type == "inpatient") %>%
    group_by(pid) %>% summarize(admit_count = n()) %>% 
    right_join(patients, by = "pid") %>% mutate(admit_count = ifelse(is.na(admit_count), 0, admit_count))
```

#### admissions count totals Just Unicare admits pre/post

Admission count for just UniCare
```{r}
pre_ibis_admissions_count %>% filter(org_name == "Unicare - Study") %>% 
    summarize(unicare_pre_admits  = sum(admit_count))

post_ibis_admissions_count %>% filter(org_name == "Unicare - Study") %>%
    summarize(unicare_post_admits = sum(admit_count))
```

#### admissions count totals- All member

Admission count total
```{r}
pre_ibis_admissions_count %>% summarize(total_admits = sum(admit_count))

post_ibis_admissions_count %>% summarize(total_admits = sum(admit_count))
```

pre/post Erik counts

```{r}
events_full  %>% 
    summarize(sum(pre_ibis_inpatient), sum(post_ibis_inpatient))

events_full %>%  filter(org_name == "Unicare - Study") %>%
    summarize(sum(pre_ibis_inpatient), sum(post_ibis_inpatient))
```

...but when I filter dates...

```{r}
events_full %>% filter(event_start_date  < ibis_coverage_start_date) %>% filter(event_start_date > coverage_start_date) %>%
    summarize(sum(pre_ibis_inpatient), sum(post_ibis_inpatient))

events_full %>% filter(event_start_date  >= ibis_coverage_start_date) %>% filter(event_start_date < ibis_coverage_end_date) %>% 
    summarize(sum(pre_ibis_inpatient), sum(post_ibis_inpatient))
```

He is counting post dates differently

#### 

#### Check counts

Patient pid 10392 9 pre and 2 post, which my counts agree with:

check also pid 13553. also agrees

```{r}
events_full %>% filter(pid == 10392) %>% select(event_type, event_start_date,
                     coverage_start_date, ibis_coverage_start_date, 
                   ibis_coverage_end_date,
                   pre_ibis_inpatient, post_ibis_inpatient) %>% filter(event_type == "inpatient")
```

```{r}
events_full %>% filter(event_start_date  <= ibis_coverage_start_date) %>% filter(event_start_date > coverage_start_date) %>%
    select(pid, event_type, event_start_date) %>%
    filter(event_type == "inpatient") %>%
    group_by(pid) %>% summarize(admit_count = n()) %>% filter(pid == 10392)

events_full %>% filter(event_start_date  > ibis_coverage_start_date) %>% filter(event_start_date < coverage_end_date) %>%
    select(pid, event_type, event_start_date) %>%
    filter(event_type == "inpatient") %>%
    group_by(pid) %>% summarize(admit_count = n()) %>% filter(pid == 10392)
```

It must be I am filtering patients out
```{r}
events_full %>% filter(pre_ibis_inpatient == 1) %>% group_by(pid) %>% summarize(count = n()) %>% summarize(sum(count))
events_full %>% filter(post_ibis_inpatient == 1) %>% group_by(pid) %>% summarize(count = n()) %>% summarize(sum(count))
```

####. Inpatient days pre/post
```{r}

#######
####### 

## pre ibis days
pre_ibis_inpatient_days <- events_full %>% filter(event_start_date  <= ibis_coverage_start_date) %>% filter(event_start_date >= coverage_start_date) %>%
    select(pid, event_type, event_start_date, event_end_date) %>%
    filter(event_type == "inpatient") %>% mutate(inpatient_days = event_end_date - event_start_date) %>%
    group_by(pid) %>% summarize(total_inpatient_days = sum(inpatient_days)) %>% 
    right_join(patients, by = "pid") %>% mutate(total_inpatient_days = ifelse(is.na(total_inpatient_days), 0, total_inpatient_days))


## post ibis days
post_ibis_inpatient_days <-events_full %>% filter(event_start_date  > ibis_coverage_start_date) %>% filter(event_start_date <= ibis_coverage_end_date) %>%
    select(pid, event_type, event_start_date, event_end_date) %>%
    filter(event_type == "inpatient") %>% mutate(inpatient_days = event_end_date - event_start_date) %>%
    group_by(pid) %>% summarize(total_inpatient_days = sum(inpatient_days)) %>% 
    right_join(patients, by = "pid") %>% mutate(total_inpatient_days = ifelse(is.na(total_inpatient_days), 0, total_inpatient_days))
```

#### Inpatient days pre/post Unicare and All member
```{r}
pre_ibis_inpatient_days %>% filter(org_name == "Unicare - Study") %>% summarize(total_days = sum(total_inpatient_days))
post_ibis_inpatient_days %>% filter(org_name == "Unicare - Study") %>% summarize(total_days = sum(total_inpatient_days))

pre_ibis_inpatient_days %>% summarize(total_days = sum(total_inpatient_days))
post_ibis_inpatient_days %>% summarize(total_days = sum(total_inpatient_days))
```

#### Check negative days

```{r}
report_full %>% filter(ibis_coverage_start_date < coverage_start_date) %>% nrow()

report_full %>% filter(ibis_coverage_start_date < coverage_start_date) %>% 
    select(coverage_start_date, ibis_coverage_start_date, ibis_coverage_end_date) %>% skim()
```

#### Coverage days pre/post Unicare and All member.

We `filter(ibis_coverage_start_date < coverage_start_date)`
```{r}
report_full %>% filter(ibis_coverage_start_date >= coverage_start_date) %>%
    mutate(pre_ibis_covered_days_check = ibis_coverage_start_date - coverage_start_date) %>% mutate(post_ibis_covered_days_check = ibis_coverage_end_date - ibis_coverage_start_date) %>% 
    select(pid, org_name, pre_ibis_covered_days_check, post_ibis_covered_days_check) %>% 
    filter(org_name == "Unicare - Study") %>% 
    summarize(unicare_pre_total = sum(pre_ibis_covered_days_check),
              unicare_post_total = sum(post_ibis_covered_days_check))

report_full %>% filter(ibis_coverage_start_date >= coverage_start_date) %>% 
    mutate(pre_ibis_covered_days_check = ibis_coverage_start_date - coverage_start_date) %>% mutate(post_ibis_covered_days_check = ibis_coverage_end_date - ibis_coverage_start_date) %>% 
    select(pid, org_name, pre_ibis_covered_days_check, post_ibis_covered_days_check) %>% 
    summarize(all_member_pre_total = sum(pre_ibis_covered_days_check), 
              all_member_post_total = sum(post_ibis_covered_days_check))
```

Check the various columns in `events_full`
```{r}
df_check <- events_full %>% select(pid, event_type, event_start_date, tablet_status, first_reminder_complete_date,
                       ibis_coverage_start_date, ibis_coverage_end_date, after_ibis_started, ibis_inpatient,
                       pre_ibis_inpatient, post_ibis_inpatient) 

df_check %>% filter(event_type == "inpatient") %>% 
    summarize(mean((event_start_date < first_reminder_complete_date) & pre_ibis_inpatient == 1))

```

#### condition barplot

```{r}
patients %>% 
  select(pid, org_name, alzheimers:urologic_cancer) %>% 
  pivot_longer(c(alzheimers:urologic_cancer), names_to = "condition", values_to = "value") %>%  mutate(org_name = if_else(org_name == "Unicare", "Unicare", "not_Unicare")) %>% 
  group_by(condition, org_name) %>%
  summarise(value = sum(value), n = n()) %>%
  mutate(prop = value / n) %>%
  ggplot(aes(x = fct_reorder(condition, -prop), y = prop, fill = org_name)) + 
  geom_col(position = "dodge") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
